Hydraulically-vulnerable trees are buffered by deep-water access in a tropical forest community

### 2020-10-24 old_ms_sections.Rmd
1. corrected italic
minor

>>>>

For each species $s$ we calculated mean mortality rate across all intervals as $\textrm{Mort}_{s,\textrm{mean}} = \frac{1}{6}\sum_{t=1}^{6} {\textrm{Mort}_{s,t}}$.

Species with deeper ERD showed lower mean mortality rates across the 35-yrs record (1982-2015; *R*^2^ = 0.11, *p* = 0.075, *n* = `r length(erd.mrate.sp)`; Fig. \@ref(fig:erd-mort)), and this relationship was stronger among evergreen species.
